---
title: "Dashboard For Problem 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(p8105.datasets)

data("instacart")
```

First of all, I intentionally filter out a subset of the original dataset to ensure a reasonable product of plots, which would not be crashed due to extremely large numbers.

```{r, warning=FALSE}
instacart =
  instacart |>
  select(reordered, order_dow, order_hour_of_day, product_name, aisle, department, days_since_prior_order) |>
  filter(department %in% c("dairy eggs", "produce", "canned goods", "beverages", "deli"))
```

Column {data-width=400}
-----------------------------------------------------------------------

### Chart A

This is a dashboard containing three plots of the dataset `instacart`.

The first plot is a bar plot that summarizes the total number of reordered goods for each department.

```{r}
instacart |>
  group_by(department) |>
  summarize(sum_of_reordered_goods = sum(reordered)) |>
  plot_ly(x = ~department, y = ~sum_of_reordered_goods, type = "bar")
```

Column {data-width=600}
-----------------------------------------------------------------------

### Chart B

The second plot is a pie chart that shows the percentage of Date of Week (from Monday to Sunday, denoted as 0-6 in order) of the goods in ordered in specific departments.

```{r}
instacart_pie = count(instacart, order_dow)

plot_ly(data=instacart_pie, values = ~n, labels = ~factor(order_dow), type = "pie") %>% layout(title="Date of Week Percentage of Specific Deparments' Ordered Goods")
```

### Chart C

The third plot is a boxplot that shows the distribution of order hour of a particular weekday for all ordered goods in the dataset. 

```{r}
instacart |>
  plot_ly(x = ~order_dow, y = ~order_hour_of_day, type = "box")
``` 